---
title: "Heart Rate of Subjects A,B,C"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
heart_rate_neurospyA<-head(read.table("/Users/athulyaajith/Desktop/heart_rate-neurospyA.csv", sep=","),1000)
heart_rate_neurospyB<-head(read.table("/Users/athulyaajith/Desktop/heart_rate-neurospyB.csv", sep=","),1000)
heart_rate_neurospyC<-head(read.table("/Users/athulyaajith/Desktop/heart_rate-neurospyC.csv", sep=","),1000)
heart_rate_neurospyA<-heart_rate_neurospyA[-1,]
heart_rate_neurospyB<-heart_rate_neurospyB[-1,]
heart_rate_neurospyC<-heart_rate_neurospyC[-1,]
require(ggplot2)
require(plotly)
```
#Subject A
```{r echo=FALSE, include=TRUE}

BaseLayerA<-ggplot(data = heart_rate_neurospyA, 
                   aes(x=as.numeric(V1),y = as.numeric(V2)))+
  ylab("Heart Rate(bpm)") +
  xlab("time(s/1000)")
ggplotly(BaseLayerA+geom_line(group=1))

```
#Subject B

```{r echo=FALSE}

BaseLayerA<-ggplot(data = heart_rate_neurospyB, 
                   aes(x=as.numeric(V1), y = as.numeric(V2)))+
  ylab("Heart Rate(bpm)") +
  xlab("time(s/1000)")
ggplotly(BaseLayerA+geom_line(group=1))

```
#Subject C

```{r echo=FALSE}

BaseLayerA<-ggplot(data = heart_rate_neurospyC, 
                   aes(x=as.numeric(V1), y = as.numeric(V2)))+
  ylab("Heart Rate(bpm)")+
xlab("time(s/1000)")
ggplotly(BaseLayerA+geom_line(group=1))

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



